---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%",
  fig.align = "center"
)
library(simply3d)
```

# {simply3d}: Convenient and fast creation of dynamic 3D Plots

This package is motivated by the fact that the plotly R package enables the creation of really awesome 3D Plots that can be dynamically viewed from all angles. This makes 3D-visualization finally useful. Sadly however the plotly syntax is not very intuitive which makes it tedious to create these plots. The functions in this package are inspired in their syntax by the base R functions plot() and curve() to make it really simple and fast to create such 3D plots.

At the moment it only includes the functions simply_scatter() which allows the easy creation of 3D scatterplots and surface() as the 3D analogue to curve(). You can also combine these two by adding a surface to a scatter plot, for example when plotting a fitted regression model. For more details please see the documentation.

## Installation

```{r, eval = FALSE}
devtools::install_github("janoleko/simply3d")
```
